Hand picking similar behaving group of customers to check clustering results

### 2021-09-13 main_old.Rmd
add structure to methodology

abstract: |
 Clustering elements based on behavior across time granularities 
bibliography: [bibliography.bib]
preamble: >
  \setlength {\marginparwidth }{2cm}
  \usepackage{mathtools,amssymb,booktabs,longtable,todonotes,amsthm}
  \def\mod{~\text{mod}~}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 4
    fig_width: 6
    fig_caption: yes
    dev: "pdf" 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
# Make sure you have the latest version of rmarkdown and bookdown
#devtools::install_github("rstudio/rmarkdown")
#devtools::install_github("rstudio/bookdown")
library(ggplot2)
library(gravitas)
library(gracsR)
library(ggdendro)
library(dplyr)
library(readr)
library(visdat)
library(ggplot2)
library(tidyverse)
library(naniar)
library(here)
library(tsibble)
library(knitr)
```

@@

## Getting data

@@

The entire data is procured from CSIRO. A subset of this data is also available from [SGSC consumer trial data](https://data.gov.au/data/dataset/smart-grid-smart-city-customer-trial-data) is available through [Department of the Environment and Energy](https://data.gov.au/data/organization/doee). It consists of the following data sets. 
_1. CustomerData:_ 78720 customers with 62 variables about them 
_2. EUDMData:_ 300 billion half-hourly consumption level data  
_3. OffersData:_ Method of contact to customer to join SGSC customer trial, either door-to-door (D2D) or via Telesales  
_4. PEResponseData:_ Peak Events response customer wise  
_5. PETimesData:_ Peak Events time stamps

@@

## Missing Data

@@

## Raw data

@@

```{r}
elec_ts <- read_rds("data/elec_ts.rds")
```

```{r raw-50, fig.height = 8, fig.cap="The raw data for 50 households are shown. It looks like there is a lot of missing values and unequal length of time series along with asynchronous periods for which data is observed."}

>>>>

abstract: |
 Clustering elements based on behavior across time granularities 
bibliography: [bibliography.bib]
preamble: >
  \setlength {\marginparwidth }{2cm}
  \usepackage{mathtools,amssymb,booktabs,longtable,todonotes,amsthm}
  \def\mod{~\text{mod}~}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 4
    fig_width: 6
    fig_caption: yes
    dev: "pdf" 
    keep_tex: yes
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
# Make sure you have the latest version of rmarkdown and bookdown
#devtools::install_github("rstudio/rmarkdown")
#devtools::install_github("rstudio/bookdown")
library(ggplot2)
library(gravitas)
library(gracsr)
library(ggdendro)
library(dplyr)
library(readr)
library(visdat)
library(ggplot2)
library(tidyverse)
library(naniar)
library(here)
library(tsibble)
library(knitr)
```

@@

## Electricity demand data

@@

### Getting data
The entire data is procured from CSIRO. A subset of this data is also available from [SGSC consumer trial data](https://data.gov.au/data/dataset/smart-grid-smart-city-customer-trial-data) is available through [Department of the Environment and Energy](https://data.gov.au/data/organization/doee). It consists of the following data sets. 
_1. CustomerData:_ 78720 customers with 62 variables about them 
_2. EUDMData:_ 300 billion half-hourly consumption level data  
_3. OffersData:_ Method of contact to customer to join SGSC customer trial, either door-to-door (D2D) or via Telesales  
_4. PEResponseData:_ Peak Events response customer wise  
_5. PETimesData:_ Peak Events time stamps

@@

### Missing Data

@@

## LGA and weather

@@

```{r,eval=FALSE}
elec_ts <- read_rds("data/elec_ts.rds")
```

```{r raw-50, fig.height = 8, fig.cap="The raw data for 50 households are shown. It looks like there is a lot of missing values and unequal length of time series along with asynchronous periods for which data is observed.", eval = FALSE}

### 2021-09-13 supplementary/algorithm2/real-data/algo2-elec100-onegran.Rmd
add structure to methodology

##----harmony-all
elec_harmony_all <- read_rds("../data/elec_harmony-100-nogap-onegran.rds")

@@

```{r cluster-characterization}
data_heatmap %>% 
  pivot_wider( names_from = quantile_prob, 
               values_from = quantile_val) %>% 
  ggplot(aes(x = category)) +  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`)) +
  facet_wrap(~group_id, ncol = 1, scales = "free_y", labeller = "label_both") +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))

>>>>

##----harmony-all
elec_harmony_all <-read_rds("../../../data/elec_harmony-100-nogap-onegran.rds")

@@

```{r cluster-characterization}
data_heatmap %>% 
  pivot_wider( names_from = quantile_prob, 
               values_from = quantile_val) %>% 
  ggplot(aes(x = category)) +  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`)) +
  facet_wrap(~group_id, ncol = 1, scales = "free_y", labeller = "label_both") +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
```

### 2021-09-13 supplementary/algorithm2/real-data/algo2-elec100.Rmd
add structure to methodology

##----harmony-all
elec_harmony_all <- read_rds("../data/algo2-rawdata-wpd.rds")

@@

elec <- read_rds("../data/elec_nogap_2013_100.rds") %>% 
  left_join(groups)%>% 
             rename ("group" = "value")

>>>>

##----harmony-all
elec_harmony_all <- read_rds("../../../data/algo2-rawdata-wpd.rds")

@@

elec <- read_rds("../../../data/elec_nogap_2013_100.rds") %>% 
  left_join(groups)%>% 
             rename ("group" = "value")

### 2021-09-13 supplementary/algorithm2/real-data/handpick_distinct_cust.Rmd
add structure to methodology

```{r read-data}
data <- read_rds("../data/elec_nogap_2013_100.rds")
```

@@

##----harmony-all
# elec <- read_rds("../data/elec_nogap_2013_100.rds") %>% filter(customer_id %in% data_pick$customer_id)
# 
# elec_split = elec %>% group_split(customer_id)
# harmonies <- read_rds("../../paper-hakear/paper/data/harmonies.rds")
# 
# harmonies_acro <- harmonies %>% mutate(facet_variable=NA, facet_levels=NA) %>% distinct()
# 
# elec_select_harmony = parallel::mclapply(1:18, function(x){
#   
#   data_id <-  elec_split %>% magrittr::extract2(x) %>% 
#     as_tsibble(index = reading_datetime)
# 
#   
#   k = hakear::select_harmonies(data_id,
#                            harmony_tbl = harmonies_acro,
#                            response = general_supply_kwh,
#                            nperm = 200,
#                            nsamp = 2
#   ) %>% mutate(customer_id = unique(data_id$customer_id))
#   #write_rds(k, paste("data/elec_harmony-100-nogap.rds"))
# }, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
# #toc()
# elec_harmny <- elec_select_harmony %>% bind_rows() 
# write_rds(elec_harmny, paste("../data/elec_harmony-100-nogap-new.rds"))

>>>>

```{r read-data}
data <- read_rds("../../../data/elec_nogap_2013_100.rds")
```

@@

##----harmony-all
elec <- read_rds("../../../data/elec_nogap_2013_100.rds") %>% filter(customer_id %in% data_pick$customer_id)

elec_split = elec %>% group_split(customer_id)
harmonies <- read_rds("../../../../paper-hakear/paper/data/harmonies.rds")

harmonies_acro <- harmonies %>% mutate(facet_variable=NA, facet_levels=NA) %>% distinct()

elec_select_harmony = parallel::mclapply(1:18, function(x){

  data_id <-  elec_split %>% magrittr::extract2(x) %>%
    as_tsibble(index = reading_datetime)

  k = hakear::select_harmonies(data_id,
                           harmony_tbl = harmonies_acro,
                           response = general_supply_kwh,
                           nperm = 200,
                           nsamp = 200
  ) %>% mutate(customer_id = unique(data_id$customer_id))
    #write_rds(k, paste("data/elec_harmony-100-nogap.rds"))
}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
#toc()
elec_harmny <- elec_select_harmony %>% bind_rows()
 write_rds(elec_harmny, paste("../../../data/elec_harmony-100-nogap-new-rerun.rds"))

f = read_rds("../../../data/elec_harmony-100-nogap-new.rds")

### 2021-09-13 supplementary/algorithm3/real-data/clean-dataset_iqr.Rmd
add structure to methodology

# library(gracsr)
# v2 <- suppressWarnings(
#   scaled_dist_gran(data, "hour_day", 
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
# 
# 
# 
# v2 <- v2 %>% arrange(dist_hod) %>% filter(customer_from!=customer_to)
# 
# write_rds(v2, "../../../data/scaled_dist_nogap_2013_100.rds")
v2 <- read_rds("../../../data/scaled_dist_nogap_2013_100.rds")

data_pick_onepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8198401) %>% 
  arrange(dist_hod) %>% 
  head(n=5)

data_pick_twopeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8181071) %>% 
  arrange(dist_hod) %>%
  head(n=5)

data_pick_threepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 11013154) %>% 
  arrange(dist_hod) %>% 
   head(n=5)

data_pick_cust <- bind_rows(
  c(data_pick_onepeak$customer_from, data_pick_onepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_twopeak$customer_from, data_pick_twopeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_threepeak$customer_from, data_pick_threepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"), .id = "design") %>% 
  filter(!(customer_id %in% c(8171227, 10183908)))

data <- read_rds("../../../data/elec_nogap_2013_100.rds")

data_pick <- data %>% filter(customer_id %in% data_pick_cust$customer_id) %>% select(customer_id,reading_datetime, general_supply_kwh) %>% left_join(data_pick_cust)

write_csv(data_pick_cust, "../../../data/data_pick_cust_clean.rds")
```

@@

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 5) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
## Do they look similar on the transformed scale?

```{r transformed-scale}
data_pick_scaled <- data_pick %>%
    group_by(customer_id) %>%
    dplyr::mutate(general_supply_kwh =  stats::qqnorm(general_supply_kwh, plot.it=FALSE)$x) %>%
    ungroup()

sm_hod <- gravitas::create_gran(data_pick_scaled, "hour_day")

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 5) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```

@@

```{r hod-only,echo = TRUE}
#quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

@@

## hod + dom
### Is the clustering sensitive to nuisance parameter?

```{r hod-dom,echo = TRUE}
#quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r clustering-result-hod-dom}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

# All 100 customers
### Running it on all 100 and making 10 clusters. Do they have sufficiently different shapes?
### Variable importance

```{r hod-100cust,echo = TRUE}
# library(gracsr)
# v2 <- suppressWarnings(
#   scaled_dist_gran(data, "hour_day", 
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")

#write_rds(v2, "../../../data/scaled_dist_100clust_deciles.rds")
v2 <- read_rds("../../../data/scaled_dist_100clust_deciles.rds")

data_dist <- v2 %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")

cust_ref <- bind_cols(customer_id=data_dist$customer_id, row = seq_len(nrow(data_dist)))

cust_rm_outlier <-   cust_ref %>% filter(!(row %in% c(73, 82, 79, 97, 25, 91)))

v3 <- v2%>% 
  filter(customer_from %in% cust_rm_outlier$customer_id,
         customer_to %in% cust_rm_outlier$customer_id)

data_dist <- v3 %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")

```

```{r hod-100cust-clustering}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

library(fpc)
# koptimal = fpc::nselectboot(as.dist(data_dist[,-1]),
#                         B = 5000,
#                         method = "ward.D",
#                         clustermethod = disthclustCBI, 
#                         classification = "averagedist",
#                         krange = 2:20)
# 
# koptimal = koptimal$kopt

groups <- tibble(group = cutree(hc, k=10), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())

data <- read_rds("../../../data/elec_nogap_2013_100.rds")
data <- data %>% left_join(groups)

sm_hod <- gravitas::create_gran(data, "hour_day")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh, group) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- unique(sm_hod_list$group)

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(group == group[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "group_serial_id")

ref_cust <- unique(sm_hod_list$group) %>% as_tibble()%>% set_names("group")  %>% 
    mutate(group_serial_id = as.character(row_number()))

sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(group_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>% 
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "group_serial_id") %>% 
  select(group_serial_id, categories_serial_id, category, everything())

# data_heatmap_100 <- sm_quantiles_ref %>% 
#  left_join(data %>% distinct(customer_id))
#

sm_quantiles_ref$group = as.factor(sm_quantiles_ref$group)

sm_quantiles_ref %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value") +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2") + scale_color_brewer(palette = "Dark2")
```
# Split these groups to see if the shapes of individual customers in a group is the same

```{r all100}
data <- read_rds("../../../data/elec_nogap_2013_100.rds")

sm_hod <- gravitas::create_gran(data, "hour_day")
sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- 1:100

data_heatmap_100 <- sm_quantiles_ref %>% 
 left_join(data %>% distinct(customer_id))

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==1) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-2")

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==2) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-2")
#+   geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==3) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-3")
#+   geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==4) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-4")
#+ geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==5) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-5")
#+geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==6) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-6")
#+ geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==7) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-7")
#+  geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==8) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-8")
#+ geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==9) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-9")
#+geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==10) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-10")
#+ geom_smooth(size = 0.5, alpha = 0.5) +
```

# Which variables are important for this clustering

I can do a ggpairs or parallel coordinate plot for this.
```{r}

data_pcp <- data_heatmap_100 %>% 
  left_join(groups)  %>% 
  select(customer_id, group, category, `50%`) %>% 
  mutate(category = as.factor(as.integer(category))) %>% 
  pivot_wider(names_from = category, values_from = `50%`) %>% 
  mutate(group = as.factor(group))

parcoord <- GGally::ggparcoord(data_pcp ,
                   columns = 3:ncol(data_pcp),
                   groupColumn = "group",
                   showPoints = FALSE, 
                   alphaLines = 0.8,
                   order = "allClass",
                   scale = "globalminmax"
) + ggplot2::theme_bw() +
  #scale_color_brewer(palette = "Dark2") + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 10)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")

ggpairs_color <- ggscatmat(data_pcp, columns=3:ncol(data_pcp)) +
  scale_colour_brewer(palette="Set2") + theme(legend.position = "bottom")
parcoord
```

```{r}
ggpairs_color
```

```{r}
pc <- prcomp(data_pcp[c(-1,-2)], center = F, scale = F)
summary(pc)
# First two principal componentsafc
comp <- data.frame(pc$x[,1:2])
data_pcp_all <- data_pcp %>% bind_cols(comp)

library(RColorBrewer)
library(scales)
data_pcp_all %>% ggplot(aes(x=PC1, y = PC2)) + geom_point(aes(color = group)) +
  #scale_color_brewer(palette = "Dark2") +
   theme_bw() + theme(legend.position = "bottom")

```

# See if month_year works for your case
# Try with two granularities

>>>>

library(gracsr)
# v2 <- suppressWarnings(
#   scaled_dist_gran_iqr(data, "hour_day",
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
# 
# 
# 
# v2 <- v2 %>% arrange(dist_hod) %>% filter(customer_from!=customer_to)
# 
# write_rds(v2, "../../../data/scaled_dist_nogap_2013_100_iqr.rds")

v2 <- read_rds("../../../data/scaled_dist_nogap_2013_100_iqr.rds")

data_pick_onepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8198401) %>% 
  arrange(dist_hod) %>% 
  head(n=7)

data_pick_twopeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8181071) %>% 
  arrange(dist_hod) %>%
  head(n=7)

data_pick_threepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8196501) %>% 
  arrange(dist_hod) %>% 
   head(n=7)

data_pick_cust <- bind_rows(
  c(data_pick_onepeak$customer_from, data_pick_onepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_twopeak$customer_from, data_pick_twopeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_threepeak$customer_from, data_pick_threepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"), .id = "design") 
#%>%   filter(!(customer_id %in% c(8171227, 10183908)))

data_pick_clust_clean <- read_rds("../../../data/data_pick_cust_clean.rds")

data <- read_rds("../../../data/elec_nogap_2013_100.rds")
# data_pick <- data %>% filter(customer_id %in% data_pick_cust$customer_id) %>% select(customer_id,reading_datetime, general_supply_kwh) %>% left_join(data_pick_cust)

data_pick <- data %>% 
  left_join(data_pick_cust %>% filter(!(customer_id %in% c(8283102, 10208156)))) %>% 
filter(customer_id %in% data_pick_cust$customer_id) %>% select(customer_id,reading_datetime, general_supply_kwh, design) 
```

@@

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
## Do they look similar on the transformed scale?

```{r transformed-scale}

sm <- robust_scale_data(data_pick, "hour_day")
v3 <- suppressWarnings(plot_data(sm, "hour_day", response = "scaled_response", nfacet = 6))
```

@@

```{r hod-only,echo = TRUE}
#quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran_iqr(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran_iqr(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

@@
